Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/ClementiBarba2020.tex
add newpage -temp fix for ref
add multirow pacakge
rework sections
add title
change bibstyle
add discussion input to main tex
edit repro sub-section
add subject areas and keywords

\begin{document}
%%%% Article title to be placed here
\title{Insert the article title here}

\author{%%%% Author details
N. C. Clementi$^{1}$, L. A. Barba$^{2}$}

%%%%%%%%% Insert author address here
\address{$^{1}$First author address\\
$^{2}$Second author address\\
$^{3}$Third author address}

%%%% Subject entries to be placed here %%%%
\subject{xxxxx, xxxxx, xxxx}

%%%% Keyword entries to be placed here %%%%
\keywords{xxxx, xxxx, xxxx}

@@

\begin{fmtext}  
\section{fist page thing}

@@

\maketitle
% Body of paper.

@@

\bibliographystyle{vancouver}
\bibliography{pygbe_rep_val} %don't leave spaces between elements, it throws error

>>>>

\begin{document}
%%%% Article title to be placed here
\title{Reproducible Validation and Replication Studies in Nanoscale Physics}

\author{%%%% Author details
N. C. Clementi$^{1}$, L. A. Barba$^{1}$}

%%%%%%%%% Insert author address here
\address{$^{1}$Department of Mechanical and Aerospace Engineering, 
The George Washington University, Washington D.C., USA }

%%%% Subject entries to be placed here %%%%
\subject{validation and verification, reproducibility and replication, computational modeling, computational physics, research software}

%%%% Keyword entries to be placed here %%%%
\keywords{reproducibility, validation, replication, nanophysics}

@@

\begin{fmtext}  
\section{Introduction}

@@

\maketitle
% Body of paper.
\section{Background and methods}\label{sec:background}
\input{background}

@@

\section{Discussion}\label{sec:discussion}
\input{discussion}

\bibliographystyle{unsrt}
\bibliography{pygbe_rep_val} %don't leave spaces between elements, it throws error
